---
title: "Spatio-temporal dynamics of *Microcystis spp.* (Cyanophyceae) blooms at Cassino Beach: origin and impact on water quality"
subtitle: Spatio-temporal dynamics of CyanoHAB's
author:
  - name: Marybeth Costilla
    email: marybeth994@gmail.com
    affiliations: 
        - id: some-tech
          name: Universidade Federal do Rio Grande
          department: Laboratorio de Cianobactérias e Ficotoxinas
          address: Street Address
          city: Rio Grande
          state: RS
          postal-code: 96203-900
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Felipe de Lucia Lobo
    email: felipelobo@ufpel.br
    affiliations:
        - id: another-u
          name: Universidade Federal de Pelotas
          department: Enghenaria Hídrica
          address: Street Address
          city: Pelotas
          state: RS
          postal-code: Postal Code
    note: |
      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
  - name: João Sarkis Yunes
    email: joaosarkis@furg.br
    affiliations:
        - ref: another-u
          name: Universidade Federal do Rio Grande
          department: Laboratorio de Cianobactérias e Ficotoxinas
          address: Street Address
          city: Rio Grande
          state: RS
          postal-code: 96203-900
    note: Yet another author footnote.

abstract: |
  *Microcystis* é um gênero de cianobactéria mundialmente conhecida por produzir hepatoxinas chamadas microcistinas (MC). Os aspectos nocivos destas florações causam eventos ecológicos e ambientais de grande impacto. Diversos estudos utilizaram imagens de satélite para realizar monitoramento da qualidade de água. Assim, imagens de satélite da Lagoa dos Patos (LP) em condições atmosféricas e hidrológicas favoráveis, identificam no espaço e tempo as florações de *Microcystis* que atingem o oceano. Portanto, o objetivo geral deste projeto é avaliar as respostas bio-óticas das florações de *Microcystis*; aplicar imagens de satélites para localizar e determinar a região de origem da espécie que atingem a praia do Cassino, estimar o conteúdo de toxinas na água e o risco à balneabilidade. Serão feitas amostragens em pontos estratégicos da saída dos Molhes ao oceano e e na praia do Cassino, para avaliar concentrações de pigmentos, número de células e identificação taxonômica. Se processarão imagens de satélite obtidas do sensor OLCI no Sentinel-3, para localizar as florações e determinar a sua origem no tempo e espaço. Além, se estimará o risco a balneabilidade da praia do Cassino usando correlações de concentrações dos pigmentos e número de células. Destacando que estas florações ocorrem próximos à os cultivos de camarões, mariscos e peixes (estação de maricultura da FURG), que por bioacumulação de cianotoxinas representam um risco por consumo a moradores e turistas. Se espera, estabelecer uma concentração de clorofila-a para balneabilidade baseado nos limites estabelecidos na CONAMA 357 e a Organização Mundial da Saúde (OMS) para águas de recreação.
keywords: 
  - AlgaeMAp
  - cianobactérias nocivas
  - ficocianina, pigmentos
  - sensoriamento remoto
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
---

Please make sure that your manuscript follows the guidelines in the 
Guide for Authors of the relevant journal. It is not necessary to 
typeset your manuscript in exactly the same way as an article, 
unless you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see   <https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>

# Bibliography styles

Here are two sample references:  @Feynman1963118 @Dirac1953888.

By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML. 
You can sets extra options with `natbiboptions` variable in YAML header. Example 

```
natbiboptions: longnamesfirst,angle,semicolon
```

There are various more specific bibliography styles available at
<https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. 
To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.

## Using CSL 

If `cite-method` is set to `citeproc` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`. In this case, the `csl` option is used to format the references. By default, this template will provide an appropriate style, but alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>. These can be downloaded
and stored locally, or the url can be used as in the example header.

# Equations

Here is an equation:
$$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$

Inline equations work as well: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

@fig-meaningless is generated using an R chunk.

```{r}
#| label: fig-meaningless
#| fig-cap: A meaningless scatterplot
#| fig-width: 5
#| fig-height: 5
#| fig-align: center
#| out-width: 50%
#| echo: false
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in @tbl-simple example.

```{r}
#| label: tbl-simple
#| tbl-cap: Caption centered above table
#| echo: true
knitr::kable(head(mtcars)[,1:4])
```

# References {-}
